P.berghei pir analysis

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
add berg biplot

```{r supp_figure_PCA_allgenes}

big_tpm_pca <-  prcomp(berghei_tpm[,-1], 
                       center = TRUE, 
                       scale. = TRUE)

@@

@@

plot_pir
```
Combining the data across the experiments.

>>>>

```{r supp_figure_PCA_allgenes}
#Set the Geneids as the berghei_tpm rownames so that the PCA function retains them as loading variables
big_tpm_pca <-  prcomp(column_to_rownames(berghei_tpm, var = 'Geneid'), 
                       center = TRUE, 
                       scale. = TRUE)

@@

# Biplot of the PCA using all genes.

```{r biplot}
pca_object_loadings <- data.frame(Geneid = rownames(big_tpm_pca$x),
                                    big_tpm_pca$x)
pca_object_loadings$Geneid <- paste0(
  pca_object_loadings$Geneid,
  ' ',
  allgene.info$Description[match(pca_object_loadings$Geneid,
                                 allgene.info$Geneid)]
)

plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005),
             inherit.aes = FALSE, size = 0.75)
```

@@

plot_pir
```

Combining the data across the experiments.
